Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-11-01 batchdedup/eval.tex
added scheduling simulation results to eval

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Read Buffer Size},
		xlabel={Read Buffer Size (MB)},
		ylabel={Backup Time},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rbufmem,y=totaltime] {figures/rbufmem.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{Backup time for verying amounts of memory allocated to disk read buffering. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffers 2.5MB, write buffer 6.25MB}
  \label{fig:mpibuf-mem}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Write Buffer Size},
		xlabel={Total Write Buffer Memory (MB)},
		ylabel={Backup Time},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=wbufmem,y=totaltime] {figures/wbufmem.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffer memory 2.5MB, Read Buffer 128KB}
  \label{fig:mpibuf-mem}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Throughput (GB/s)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rounds,y=throughput] {figures/sim_full.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{simulated results for average throughput for individual VMs in 100 node cluster.}
  \label{fig:mpibuf-mem}
\end{figure}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Average Backup Time (min)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rounds,y expr=(\thisrow{avgbackuptime})/60] {figures/sim_full.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{simulated results for average vm backup time for individual VMs in 100 node cluster.}
  \label{fig:mpibuf-mem}
\end{figure}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Average Turnaround Time (min)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rounds,y expr=(\thisrow{turnaround})/60] {figures/sim_full.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{simulated results for average vm turnaround time for individual VMs in 100 node cluster.}
  \label{fig:mpibuf-mem}
\end{figure}

%\begin{figure}[ht]
%  \centering
%	\begin{tikzpicture}
%		\begin{axis}[
%		%title={Read Buffer Size},
%		xlabel={Read Buffer Size (MB)},
%		ylabel={Backup Time},
%		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
%		%legend pos=north west
%		]
%                \addplot table[x=rbufmem,y=totaltime] {figures/rbufmem.txt};
%                %\legend{Total Backup Time};
%		\end{axis}
%	\end{tikzpicture}
%  \caption{Backup time for verying amounts of memory allocated to disk read buffering. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffers 2.5MB, write buffer 6.25MB}
%  \label{fig:mpibuf-mem}
%\end{figure}
%
%\begin{figure}[ht]
%  \centering
%	\begin{tikzpicture}
%		\begin{axis}[
%		%title={Write Buffer Size},
%		xlabel={Total Write Buffer Memory (MB)},
%		ylabel={Backup Time},
%		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
%		%legend pos=north west
%		]
%                \addplot table[x=wbufmem,y=totaltime] {figures/wbufmem.txt};
%                %\legend{Total Backup Time};
%		\end{axis}
%	\end{tikzpicture}
%  \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffer memory 2.5MB, Read Buffer 128KB}
%  \label{fig:mpibuf-mem}
%\end{figure}
